Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Added optimization thoughts to conclusion
Added some analysis of results

\subsection{Small files}
For small files, 1B and 1KB, we can clearly see that both \ac{SHA}-256 and
double \ac{SHA}-256 greatly outperforms the \ac{SHA}-3 candidate
implementations, which is unexpected if the time Tahoe-\ac{LAFS} do mainly
realy on the filesize.

\subsection{Large inputs}

\subsection{The candidates}

\subsection{Optimizing results}

>>>>

\subsection{Small files}
For small files, 1B and 1KB, we can clearly see that both double \ac{SHA}-256 
greatly outperforms the \ac{SHA}-3 candidate implementations. The data being 
hashed for these files are dominated by lengths of 63 and 106 bytes. By 
comparing with \ac{SUPERCOP} results, and especially the fact that we are 
using double \ac{SHA}-256, which should result in large overhead this is
unexpected.

\subsection{Large files}
For large files, 1MB, 100MB and 1GB, some of the \ac{SHA}-3 candidates are 
actually outperforming double \ac{SHA}-256, which is expected from the
\ac{SUPERCOP} results. However if we compare this result with the result for
small files, and expect that a hash algorithm should do better on a cycles/byte
basis when hashing larger data values this is not expected. Data sizes which
are hashed during 1GB and 100MB up/downloads are dominated by 101B, 65569B and
131106B. 50\% of the hashes are done on 101B, which is a size which should be
largely affected by having to do double SHA-256. However, since the small files
had a similar percentage of operations being done on 106B chunks, blaming need
to use double \ac{SHA}256 is not enough. It looks like indeed the large data
chunks being hashed is what is making the difference.

\subsection{The candidates}
If we look primarily at the large file up/download we see that the candidates
that outperforms, or are close to outperforming \ac{SHA}-256 are BLAKE,
\ac{BMW}, Shabal, Simd and Luffa. This is expected and corresponds with the
results from \ac{SUPERCOP}.

\subsection{Final round candidates}
BLAKE, Keccak, Skein, Grøstl and JH have made it through to the final round of
the \ac{SHA}-3 competition. %TODO: some comments on theese

\subsection{Optimizing results}
We have not used the fastest possible implementations possible for various
reasons mentioned previously. However, if we had actually used the fastest
implementations in \ac{SUPERCOP}, achieved median speed for every hash
calculated the results should look as in Table X. The table is calculated using
the lengths of data actually hashed by Tahoe-\ac{LAFS}, the medians from
\ac{SUPERCOP} results, and interpolation for sizes in between those mentioned in
\ac{SUPERCOP}. The point of this result is to see the maximum performance gain
possible for TAHOE-\ac{LAFS} by adopting one of the current \ac{SHA}-3
candidate implementations.

%TODO: Optimaliserte resultater tabell
